{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-28 paper/paper.tex
s/undefined/unspecified
fixed wording

\begin{itemize}
\item \textit{Explicit and implicit flows}: In an explicit flow the information is leaked
      directly into some public variable (e.g. $l := h$), while in implicit flows the information
      is leaked through the control structure of the program (e.g. $\text{if}\ h = 1\ \text{then}\ l := 1\ \text{else}\ l := 0$).
\item \textit{Probabilistic channels}: If an attacker is able to run a computation multiple times
      he might be able to obtain information by looking at the probability distribution of the
      public outputs.
\item \textit{Power channels}: If the attacker has physical access to the computer or at least figure out
      the power consumption, he might be able to obtain data through the changing power consumption.
\item \textit{Resource exhausting channels}: Information also may be leaked through the exhaustion
      of finite (mostly physical) resources (e.g. a buffer overflow).
\item \textit{Termination channels}: The attacker can obtain information through the termination
      or non-termination of the computation or program.
\item \textit{Timing channels:} Information can be obtained through the time at which this action
      occurs. On the one hand \textit{external} timing channels cover the action like the termination
      of the program, where the attacker obtains information from the total execution time of the program.
      On the other hand \textit{internal} timing channels are occur in multithreaded programs through the timing difference
      between threads. For example the two threaded (modeled with $||$) program \[\text{if}\ h = 1\ \{\text{sleep}(100)\}\ ;\ l := 1\ ||\ \text{sleep}(50)\ ;\ l := 0\]
      executed with most schedulers will leak the information of $h$ into $l$ through the timing difference
      if $h = 1$.
\end{itemize}

@@

Now the instantiation of the framework is complete, except for the scheduler which was left undefined
in the paper.

>>>>

\begin{itemize}
\item \textit{Explicit and implicit flows}: In an explicit flow the information is leaked
      directly into some public variable (e.g. $l := h$), while in implicit flows the information
      is leaked through the control structure of the program (e.g. $\text{if}\ h = 1\ \text{then}\ l := 1\ \text{else}\ l := 0$).
\item \textit{Probabilistic channels}: If an attacker is able to run a computation multiple times
      he might be able to obtain information by looking at the probability distribution of the
      public outputs.
\item \textit{Power channels}: If the attacker has physical access to the computer or at least figure out
      the power consumption, he might be able to obtain data through the changing power consumption.
\item \textit{Resource exhausting channels}: Information also may be leaked through the exhaustion
      of finite (mostly physical) resources (e.g. a buffer overflow).
\item \textit{Termination channels}: The attacker can obtain information through the termination
      or non-termination of the computation or program.
\item \textit{Timing channels:} Information can be obtained through the time at which this action
      occurs. On the one hand \textit{external} timing channels cover the action like the termination
      of the program, where the attacker obtains information from the total execution time of the program.
      On the other hand \textit{internal} timing channels are occur in multithreaded programs through the timing difference
      between threads. For example the two threaded (denoted with $||$) program \[\text{if}\ h = 1\ \{\text{sleep}(100)\}\ ;\ l := 1\ ||\ \text{sleep}(50)\ ;\ l := 0\]
      executed with most schedulers will leak the information of $h$ into $l$ through the timing difference
      if $h = 1$.
\end{itemize}

@@

Now the instantiation of the framework is complete, except for the scheduler which was left unspecified
in the paper.
